Shapes of dust waves, bow waves, and bow shocks

### 2017-11-23 papers/Paper1/dusty-bow-wave.tex
Change title and intro for paper 2

\title[Dusty bow wave shapes]
{True versus apparent shapes of dusty radiative bow waves}

@@

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  Dusty stellar bow waves result from the action of a star's radiation
  pressure on a stream of dust grains that is flowing past it.  They
  are an alternative mechanism to hydrodynamic bow shocks for
  explaining the curved arcs of infrared emission seen around some
  stars.  We develop simple cylindrically symmetric models for the
  dust grain dynamics under the influence of radiation and gas--grain
  drag forces, which produce bow shapes that we call dragoids.  Using
  our recently developed two-dimensional classification scheme for
  projected bow shapes, we then analyze the inclination-dependent
  tracks of the dragoids in the planitude--alatude plane, finding
  interesting differences from the wilkinoid, cantoid, and ancantoid
  shapes of hydrodynamic bow shock models. We further show how these
  are modified in the presence of small-amplitude standing-wave
  oscillations of the basic shape, as may be produced by hydrodynamic
  instabilities or a time-varying source.  We analyze the prospects of
  using shape analysis of observational datasets to discriminate
  between different bow models, finding that sample sizes of order 100
  are required.
\end{abstract}

>>>>

\title[Dust waves, bow waves, bow shocks]
{Shapes of dust waves, bow waves, and bow shocks}

@@

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  Dust waves and bow waves result from the action of a star's
  radiation pressure on a stream of dust grains that is flowing past
  it.  They are an alternative mechanism to hydrodynamic bow shocks
  for explaining the curved arcs of infrared emission seen around some
  stars.  We employ simple cylindrically symmetric models for the dust
  grain dynamics under the influence of radiation and weak gas--grain
  coupling, which produce bow shapes that we call dragoids.  We also
  show how thin-shell hydrodynamic models can be modified to treat the
  case of strong gas-grain coupling, producing bow shapes that we call
  trapoids.  Using our recently developed two-dimensional
  classification scheme for projected bow shapes, we then analyze the
  inclination-dependent tracks of the dragoids and trapoids in the
  planitude--alatude plane, finding interesting differences from the
  wilkinoid, cantoid, and ancantoid shapes of hydrodynamic bow shock
  models. We further show how these are modified in the presence of
  small-amplitude standing-wave oscillations of the basic shape, as
  may be produced by hydrodynamic instabilities or a time-varying
  source.  We analyze the prospects of using shape analysis of
  observational datasets to discriminate between different bow models,
  finding that sample sizes of order 100 are required.
\end{abstract}

### 2017-11-23 papers/Paper1/sec-dust-bow-intro.tex
Change title and intro for paper 2

Curved emission arcs around stars \citep[e.g.,][]{Gull:1979a} are
often interpreted as bow shocks, due to a supersonic hydrodynamic
interaction between the star's wind and an external stream. This
stream may be due to the star's own motion or to an independent flow,
such as an \hii{} region in the champagne phase
\citep{Tenorio-Tagle:1979a}, or another star's wind
\citep{Canto:1996}. However, an alternative interpretation in some
cases may be a radiation-pressure driven bow wave, as first proposed
by \citet[\S\textsc{vi}]{van-Buren:1988a}.  In this scenario, photons
emitted by the star are absorbed by dust grains in the incoming
stream, with the resultant momentum transfer being sufficient to
decelerate and deflect the grains within a certain distance from the
star, forming a dust-free, bow-shaped cavity with an enhanced dust
density at its edge.  Two regimes are possible, depending on the
strength of coupling between the gas (or plasma) and the dust.  In the
strong-coupling regime, gas--grain drag decelerates the gas along with
the dust, forming a shocked gas shell in a similar fashion to the
wind-driven bow shock case.  In the weak-coupling regime, the gas
stream is relatively unaffected and the dust temporarily decouples to
form a dust-only bow wave.  This second case has recently been studied
in detail in the context of the interaction of late O-type stars
(which have only weak stellar winds) with dusty photoevaporation flows
inside \hii{} regions \citep{Ochsendorf:2014a, Ochsendorf:2014b,
  Ochsendorf:2015a}.  More complex, hybrid scenarios are also
possible, such as that studied by \citet{van-Marle:2011a}, where a
hydrodynamic bow shock forms, but the larger dust grains that
accompany the stellar wind pass right through the shocked shell due to
weak gas--grain coupling, and form their own bow wave at a larger
radius.

In \citet[][hereafter \PaperI{}]{Tarango-Yong:2018a}, we proposed a
new two-dimensional classification scheme for bow shapes: the
projected planitude--alatude, or \(\Pi'\)--\(\Lambda'\), diagram.  Planitude
measures the flatness of the bow's apex, while alatude measures the
openness of the bow's wings.  Both are dimensionless ratios of lengths
that can be estimated from observational images.  We have analyzed the
inclination-dependent tracks on the \(\Pi'\)--\(\Lambda'\) plane for simple
geometric shapes (spheroids, paraboloids, hyperboloids) and for
thin-shell hydrodynamic bow shock models (wilkinoid, cantoids,
ancantoids).  In this paper, we will do the same for simple models of a
dusty radiation bow wave in the weak coupling limit (dragoids).

>>>>

Curved emission arcs around stars \citep[e.g.,][]{Gull:1979a} are
often interpreted as \textit{bow shocks}, due to a supersonic
hydrodynamic interaction between the star's wind and an external
stream. This stream may be due to the star's own motion or to an
independent flow, such as an \hii{} region in the champagne phase
\citep{Tenorio-Tagle:1979a}, or another star's wind
\citep{Canto:1996}. However, an alternative interpretation in some
cases may be a radiation-pressure driven bow wave, as first proposed
by \citet[\S\textsc{vi}]{van-Buren:1988a}.  In this scenario, photons
emitted by the star are absorbed by dust grains in the incoming
stream, with the resultant momentum transfer being sufficient to
decelerate and deflect the grains within a certain distance from the
star, forming a dust-free, bow-shaped cavity with an enhanced dust
density at its edge.  Two regimes are possible, depending on the
strength of coupling between the gas (or plasma) and the dust.  In the
strong-coupling regime, gas--grain drag decelerates the gas along with
the dust, forming a shocked gas shell in a similar fashion to the
wind-driven bow shock case.  In the weak-coupling regime, the gas
stream is relatively unaffected and the dust temporarily decouples to
form a dust-only shell.  This second case has recently been studied in
detail in the context of the interaction of late O-type stars (which
have only weak stellar winds) with dusty photoevaporation flows inside
\hii{} regions \citep{Ochsendorf:2014a, Ochsendorf:2014b,
  Ochsendorf:2015a}.  We follow the nomenclature proposed by
\citet{Ochsendorf:2014b}, in which \textit{dust wave} refers to the
weak coupling case and \textit{bow wave} to the strong coupling case.
More complex, hybrid scenarios are also possible, such as that studied
by \citet{van-Marle:2011a}, where a hydrodynamic bow shock forms, but
the larger dust grains that accompany the stellar wind pass right
through the shocked gas shell, and form their own dust wave at a
larger radius.

\begin{figure}
  \centering
  \framebox{
    \parbox[m][4cm]{0.8\linewidth}
    {\centerline{\textbf{\dotfill TODO\dotfill}}}}
  \caption{Bow shocks, bow waves, and dust waves}
  \label{fig:3-types-bow}
\end{figure}

In \citet[][hereafter \PaperI{}]{Tarango-Yong:2018a}, we proposed a
new two-dimensional classification scheme for bow shapes: the
projected planitude--alatude, or \(\Pi'\)--\(\Lambda'\), diagram.  Planitude
measures the flatness of the bow's apex, while alatude measures the
openness of the bow's wings.  Both are dimensionless ratios of lengths
that can be estimated from observational images.  We have analyzed the
inclination-dependent tracks on the \(\Pi'\)--\(\Lambda'\) plane for simple
geometric shapes (spheroids, paraboloids, hyperboloids) and for
thin-shell hydrodynamic bow shock models (wilkinoid, cantoids,
ancantoids).  In this paper, we will do the same for simple models of
radiation-driven dust waves (dragoids) and bow waves (trapoids).
